Embedding Intuitionistic into Classical Logic

### 2022-07-16 CSL/lipics-v2021-EIICL.tex
todo removed
appendix small corrections

It is straight-forward to extend structures to the additional symbols such that the formulas $S^+(\varphi)\cup\mathcal S^-(\varphi)$ are satisfied, i.e. for each structure $\mathcal M$ and formula $\varphi$ we can define a structure $\mathcal S(\mathcal M, \varphi)$, whose exact definition can be found in the appendix as Definition~\ref{def:transf-structure}, such that:
\begin{lemma}
For every formula $\varphi$ and structure $\mathcal M$, we have that	$\mathcal S(\mathcal M, \varphi)\models\mathcal S^+(\varphi)\cup S^-(\varphi)$.
\end{lemma}

\begin{lemma}
	For every structure $\mathcal M$,
	$\mathcal M\models \varphi$ if and only if $S(\mathcal M, \varphi)\models P_\varphi$.
\end{lemma}

@@

\begin{lemma}\label{ap2}
	For every structure $\mathcal M$ and $\{t_1\dots t_n\} = T$ that contains all free variables in $\chi$ and variable assignment $v$
	\begin{itemize}
		\item if $\mathcal M, v\models\varphi^S_T$ then $\mathcal M, v\models \varphi$
		\item if $\mathcal M, v\not\models\varphi^H_T$ then $\mathcal M, v\not\models\varphi$.
	\end{itemize}
\end{lemma}

@@

	1. $\chi = \varphi\to\psi$. Suppose $\mathcal M, v\models\chi^S_T$, i.e. $\mathcal M, v\not\models\varphi^H_T$ or $\mathcal M, v\models\psi^S_T$. By induction hypothesis $\mathcal M, v\not\models \varphi$ or $\mathcal M, v\models\psi$, i.e. $\mathcal M, v\models \chi$. On the other hand suppose $\mathcal M, v\not\models\chi^H_T$, i.e. $\mathcal M, v\models\varphi^S_T$ and $\mathcal M, v\not\models\varphi^H_T$. Again by induction hypothesis $\mathcal M,v\models\varphi$ and $\mathcal M, v\not\models \varphi$, so $\mathcal M, v\not\models\chi$.

@@

	4. $\chi = \forall x\varphi$.  Suppose $\mathcal M, v\models\chi^S_T$, i.e. for all $m\in M$ we have $\mathcal M, v[m/a]\models \chi[a/x]^S_{T\cup\{a\}}$ and by induction hypothesis $\mathcal M, v[m/a]\models \chi[a/x]$. Then it follows that $\mathcal M, v\models\varphi$. On the other hand suppose $\mathcal M, v\not\models\chi^H_T$, i.e. there exists $m\in M$ such that $\mathcal M, v[m/a]\not\models\chi[a/x]^H_{T\cup \{a\}}$, then by induction hypothesis $\mathcal M, v[m/a]\not\models \chi[a/x]$, i.e. $\mathcal M, v\not\models\forall x\chi$.

@@

>>>>

It is straight-forward to extend structures to the additional symbols such that the formulas $S^+(\varphi)\cup\mathcal S^-(\varphi)$ are satisfied, i.e. for each structure $\mathcal M$ and formula $\varphi$ we can define a structure $\mathcal S(\mathcal M, \varphi)$, whose exact definition can be found in the appendix as Definition~\ref{def:transf-structure}, such that:
\begin{lemma}\label{thm:struct1}
For every formula $\varphi$ and structure $\mathcal M$, we have that	$\mathcal S(\mathcal M, \varphi)\models\mathcal S^+(\varphi)\cup S^-(\varphi)$.
\end{lemma}

\begin{lemma}\label{thm:struct2}
	For every structure $\mathcal M$,
	$\mathcal M\models \varphi$ if and only if $S(\mathcal M, \varphi)\models P_\varphi$.
\end{lemma}

@@

\begin{lemma}\label{ap2}
	For every structure $\mathcal M$ and $\{z_1\dots z_n\} = Z$ that contains all free variables in $\chi$ and variable assignment $v$
	\begin{itemize}
		\item if $\mathcal M, v\models\varphi^S_Z$ then $\mathcal M, v\models \varphi$
		\item if $\mathcal M, v\not\models\varphi^H_Z$ then $\mathcal M, v\not\models\varphi$.
	\end{itemize}
\end{lemma}

@@

	1. $\chi = \varphi\to\psi$. Suppose $\mathcal M, v\models\chi^S_Z$, i.e. $\mathcal M, v\not\models\varphi^H_Z$ or $\mathcal M, v\models\psi^S_Z$. By induction hypothesis $\mathcal M, v\not\models \varphi$ or $\mathcal M, v\models\psi$, i.e. $\mathcal M, v\models \chi$. On the other hand suppose $\mathcal M, v\not\models\chi^H_Z$, i.e. $\mathcal M, v\models\varphi^S_T$ and $\mathcal M, v\not\models\varphi^H_Z$. Again by induction hypothesis $\mathcal M,v\models\varphi$ and $\mathcal M, v\not\models \varphi$, so $\mathcal M, v\not\models\chi$.

@@

	4. $\chi = \forall x\varphi$.  Suppose $\mathcal M, v\models\chi^S_Z$, i.e. for all $m\in M$ we have $\mathcal M, v[m/a]\models \chi[a/x]^S_{Z\cup\{a\}}$ and by induction hypothesis $\mathcal M, v[m/a]\models \chi[a/x]$. Then it follows that $\mathcal M, v\models\varphi$. On the other hand suppose $\mathcal M, v\not\models\chi^H_Z$, i.e. there exists $m\in M$ such that $\mathcal M, v[m/a]\not\models\chi[a/x]^H_{Z\cup \{a\}}$, then by induction hypothesis $\mathcal M, v[m/a]\not\models \chi[a/x]$, i.e. $\mathcal M, v\not\models\forall x\chi$.

@@

Lemmas~\ref{thm:struct1} and~\ref{thm:struct2} then follow directly by induction on the height of $\varphi$.
